### 2015-01-12 paper/Content/02research.tex
Minor corrections
minor changes

\section{Research}
\label{sec:research}

% MVP applied to Android Apps

\IEEEPARstart{I}{n} this chapter, the questions are answered by research. Blablablabalabalaba.
\todo[inline]{Change me}

Before we elaborate how we applied the MVP approach to our prototype

In the next section we show in detail how we applied that shit

@@

\subsection{Problems in Android Development (detailed)}

>>>>

\section{Research}
\label{sec:research}
\todo[inline]{Change title?}
\IEEEPARstart{B}{efore} the application prototype is built, composing components of \emph{Android} applications are introduced in this chapter. In addition, it is shown why the MVP approach may improve app development and what MVP actually is.
% MVP applied to Android Apps

@@

\subsection{Problems in Android Development (detailed)}
\todo[inline]{Change heading and add text here}
